\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}}%
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=3500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf}}\\[2mm]%
\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}%
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}}%
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}\\[2mm]%
\subfigure[flow at t=4000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}}%
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}}\\[2mm]%
\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}%
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}}\\[2mm]%
\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}}%
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=2000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf}}\\[2mm]%
\subfigure[flow at t=3000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}}%
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}}\\[2mm]%
\subfigure[flow at t=24000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}}%
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/map_of_boundaries.pdf}\label{a}}
\subfigure[permeabilities using an unstructured and fixed computational domain]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{b}}
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{center}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=250 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}}\\[2mm]%
\subfigure[flow at t=250 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}}%
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}}\\[2mm]%
\subfigure[flow at t=500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}}%
\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t=1500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}}\\[2mm]%
\subfigure[flow at t=1500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}}%
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

\begin{figure}
\centering
\subfigure[flow at t= end (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}}\\[2mm]%
\subfigure[flow at t= end (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}}%
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
\subfigure[flow at start]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
\label{fig:3testcase_a}
\end{figure}

\begin{comment}
\begin{figure}
\makebox[\textwidth]{%
\subfigure[[MR10 fixed mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh t=1500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh t=1500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh t=7500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh t=7500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}%
}%
\hfill    
\subfigure[MR10 fixed adapt end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}%
}}%
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
%\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
\label{fig:3testcase}
\end{figure}

%\end{comment}

\begin{figure}[htbp]                
\centering
\includegraphics{./Pics1/5reg_dinlet_fixed_500.pdf}
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

>>>>

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end   
}
}     
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=250   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

\begin{figure}
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

@@

%\begin{figure}[h]
%\vbox{
%\hbox{\hspace{3.5cm}
%\includegraphics[width=.5\textwidth]{} 
%}
%\vspace{0.0cm}
%\hbox{\hspace{5.0cm} (a)    
%}
%\vspace{0.25cm}
%\hbox{\hspace{3.5cm}
%\includegraphics[width=.5\textwidth]{}
%}
%\vspace{0.0cm}
%\hbox{\hspace{5.0cm} (b)      
%}
%}     
%\caption{}
%\label{}
%\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/map_of_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilities   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at start      
}
}     
\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR10 fixed mesh start    
}
\vspace{0.25cm}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 adapt mesh start     
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) MR10 fixed mesh t=1500      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (d) MR10 adapt mesh t=1500     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (e) MR10 fixed mesh t=7500    
}
\vspace{0.25cm}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (f) MR10 adapt mesh t=7500      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (g) MR10 fixed mesh end      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end]     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:3testcase_b}
\end{figure}

\begin{figure}                
\centering
\includegraphics{./Pics1/5reg_dinlet_fixed_500.pdf}
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}
